% bibliography
\newpage
\begin{thebibliography}{99}
\setlength{\baselineskip}{12pt}% resets spacing to single space

\addcontentsline{toc}{section}{References}  %This command adds the Bibliography to the Table of Contents.

%an article in a journal
\bibitem{boas} {\sc R. P. Boas}, ``Can We Make Mathematics
Intelligible?", {\em Amer. Math. Monthly} 88(1981),
pp.727-731.

%a page on a website
\bibitem{devlin} {\sc Keith Devlin}, ``Staying the
Course'', {\em MAA Online}, Mathematical Association of
America, June 2005, 29 June 2005, Devlin's Angle,
\verb+<http://www.maa.org/devlin/devlin_06_05.html>+.

%a book
\bibitem{gillman} {\sc Leonard Gillman}, {\em Writing
Mathematics Well}, The Mathematical Association of
America, 1987.

% a page on a website (author not known)
\bibitem{latexhelp}{\em Goddard Institute for Space
Studies}, NASA Goddard Institute for Space Studies at
Columbia University, 4 August 2005, Hypertext Help with
LaTeX, \verb+<http://www.giss.nasa.gov/latex/index.html>+.

%a book
\bibitem{goossens}{\sc Michel Goossens, Frank Mittelbach,
Alexander Samarin}, {\em The LATEX Companion},
Addison-Wesley, 1994.

%a wesite
\bibitem {symbols} {\sc Sheldon Green}, {\em Hypertext Help
with LaTeX},NASA, 15 May 1997, 12 July 2005,
\verb+<http://www.giss.nasa.gov/latex/index.html>+.

%an article in a collection (book)
\bibitem{halmos}{\sc Paul R. Halmos}, ``How to Write
Mathematics'',
in {\em Selecta, Expository Writing}, Springer, 1983, pp.157-186.

% a web page - author known
\bibitem{online}{\sc Andrew Harnack, Eugene Kleppinger}, "Using MLA Style
to Cite and Document Sources", in
{\em online!: a reference guide to using online sources},
Bedford/St.Martin's, 2003, 28 June, 2005.
\verb+<http://www.bedfordstmartins.com/online/cite5.html#1>+.

%a book
\bibitem{lamport} {\sc Leslie Lamport},{\em Latex: A
Document Preparation System: User's Guide and Reference
Manual}, Addison-Wesley, 1985.

%a book
\bibitem{lamport} {\sc Leslie Lamport},{\em Latex: A
Document Preparation System: User's Guide and Reference
Manual}, Addison-Wesley, 1985.

%a website - organization known
\bibitem{maa:undergrad} {\em MAA Online}, 2005,
Mathematical Association of America, 29 June 2005,
Information for Undergraduate Students,
\verb+<http://www.maa.org/students/undergrad/>+.
\end{thebibliography} 

